Stochastic Variance Reduced Policy Gradient

### 2018-02-02 svrpg.tex
Correction Pratical Variant parts
correzioni

\section{Hyperparameters}\label{sec:stopping}
In Reinforcement learning we have to take into account the gradient's variance.
\todomat{$\uparrow$ the opening of the section could connect better with previous sections. Declare which meta-parameters will be addressed in the section}
A common way to reduce the effect of variance is to use Adaptive Moment Estimation (Adam) \cite{kingma2014adam}, a method that computes adaptive learning rates for each parameter. Adam helps to stabilize the gradient estimate by computing adaptive learning rates for each parameter based on the history of the gradients' variance.
Due to this feature we can use two different adam in order to properly leverage the structure of the proposed SVRPG update. The first adam will be associated to the snapshot updates and the second one will be associated to the sub-iteration updates. By doing so we are decoupling the contribution to the variance introduced by the snapshots from that one introduced by the sub-iterations. These two variance contributions lie, respectively, on two different order of magnitude because the number of trajectories used to perform the estimates for the snapshot is greater than that used for a sub-iteration.Therefore, using two adam optimizers allows us to properly adapt the learning rate in each situation. 
Denote by $\alpha_{snap}$ the learning rate associated to the last snapshot and denote by  $\alpha_{sub-iter}$ the learning rate associated to the current sub-iteration.

As shown in Section \ref{sec:conv}, the performance of the SVRPG algorithm is sensitive to the epoch size $m$.
As the number of sub-iterations increases, the variance of the importance weights and the gradient increases too.
Therefore, the SVRPG algorithm fails in its primary aim of stabilizing the gradient estimate.
A fixed epoch size is not the optimal choice.
Few sub-iterations lead to few updates, many update lead to increases of variance.

In order to cope with this behaviour we introduce an adaptive stopping condition: we permorm a new snapshot anytime the weighted learning rate proposed by the adam optimizer in a sub-iteration is smaller than the weighted one proposed at the immediately previous snapshot. This stopping condition is subject to a constraint on the maximum number of sub-iterations performable, which is problem dependent.
More precisely we stop performing sub-iterations when:

>>>>

\section{Hyperparameters}\label{sec:stopping}
In section \ref{sec:conv}, we introduced the practical need to properly choose $\alpha$ and $m$, which are, respectively, the step size and the number of sub-iterations to perform after a snapshot. The first one is crucial to balance the variance introduced by estimations within sub-iterations with respect to the variance introduced by estimations associated to the snapshots. The second one is essetial to control the variance introduced by the importance weights, mainly because the farther you go from the snapshot policy the higher the variance of the importance weights will be.

A common way to reduce the effect of variance is to use Adaptive Moment Estimation (Adam) \cite{kingma2014adam}, a method that computes adaptive learning rates for each parameter. Adam helps to stabilize the gradient estimate by computing adaptive learning rates for each parameter based on the history of the gradients' variance.
Due to this feature we can use two different adam in order to properly leverage the structure of the proposed SVRPG update. The first adam will be associated to the snapshot updates and the second one will be associated to the sub-iteration updates. By doing so we are decoupling the contribution to the variance introduced by the snapshots from that one introduced by the sub-iterations. These two variance contributions lie, respectively, on two different order of magnitude because the number of trajectories used to perform the estimates for the snapshot is greater than that used for a sub-iteration.Therefore, using two adam optimizers allows us to properly adapt the learning rate in each situation. For the above mentioned reasons let us denote by $\alpha_{snap}$ the learning rate associated to the last snapshot and by  $\alpha_{sub-iter}$ the learning rate associated to the current sub-iteration.

We have already said that as the number of sub-iterations $m$ increases the variance of the importance weights increases too. Therefore, the SVRPG algorithm fails in its primary aim of stabilizing the gradient estimate.

We have seen, sperimentally, that a fixed epoch size is not the optimal choice, but an adaptive one would better exploit the total amount of data at hand. Hence, we permorm a new snapshot anytime the weighted learning rate proposed by the adam optimizer in a sub-iteration is smaller than the weighted one proposed at the immediately previous snapshot. This stopping condition is subject to a constraint on the maximum number of sub-iterations performable, which is problem dependent.
More precisely we stop performing sub-iterations when:
